---
title: "Use Pre-Built Inputs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use Pre Built Inputs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hectordata)
library(hector)
library(ggplot2)
```

`hectordata` contains several pre-built input files for [Hector](https://github.com/jgcri/hector). In this exmaple we will cover how to use these input files to run [Hector](https://github.com/jgcri/hector).


Start out by taking a look at the pre-built ini files included in `hectordata` using the `system.file` call. 

```{r}
hectordata_dir <- system.file("input",  package = "hectordata")
list.files(hectordata_dir, pattern = ".ini")
```



Let's run hector for the ssp119, ssp460, and ssp585 scenarios. Start by defining the path to the ini files. 

```{r}
ini_ssp119 <- system.file("input/hector_ssp119.ini", package = "hectordata")
ini_ssp460 <- system.file("input/hector_ssp460.ini", package = "hectordata")
ini_ssp585 <- system.file("input/hector_ssp585.ini", package = "hectordata")
```


Set up the hector cores. 

```{r}
core_ssp119 <- newcore(ini_ssp119, name = "ssp119")
core_ssp460 <- newcore(ini_ssp460, name = "ssp460")
core_ssp585 <- newcore(ini_ssp585, name = "ssp585")
```


Run hector.

```{r}
run(core_ssp119)
run(core_ssp460)
run(core_ssp585)
```

Get the results for global mean temp for each run. 

```{r}
dates <- 1850:2100
var <- GLOBAL_TEMP()

dat1 <- fetchvars(core_ssp119, dates, var)
dat2 <- fetchvars(core_ssp460, dates, var)
dat3 <- fetchvars(core_ssp585, dates, var)

data <- rbind(dat1, dat2, dat3)
```


Plot the results.

```{r}
ggplot(data) + 
  geom_line(aes(year, value, color = scenario)) + 
  labs(title = "Hector Global Mean Temp.", 
       y = expression(~degree~"C"), 
       x = "Year")
```



Shutdown Hector cores 

```{r, results='hide'}
shutdown(core_ssp119)
shutdown(core_ssp460)
shutdown(core_ssp585)
```

